---
output: markdown
knit: ragnar:::run_chat_sheet
---

```{r, echo = FALSE}
knitr::opts_chunk$set(comment = '', echo = FALSE)

library(ellmer)
chat <- ellmer::chat_ollama(model = "qwen3:4b")
```

# System

You are an expert R programmer and mentor.

```{r, echo = FALSE}
get_current_weather <- function(location = "") {
  list(temp = 65, conditions = "sunny")
}

chat$register_tool(
  tool_def = tool(
    get_current_weather,
    "Get the current weather",
    location = type_string(
      "location name. If missing, defaults to the current user location",
      required = TRUE
    )
  )
)
```

# User

What is the current weather in new york?

# LLM

```{tool}
get_current_weather(location = "New York")
```

```{r}

```

# LLM

<think> Okay, the user asked for the current weather in New York. I
called the get_current_weather function with location set to New York.
The response came back with a temperature of 65 and sunny conditions.
Now I need to present this information in a clear and friendly way. Let
me check if there are any other details I should include, but the
response only has temp and conditions. I'll format it into a sentence
that answers their question directly. Make sure to mention both the
temperature and the weather condition. Also, maybe add a polite closing
statement. Alright, that should cover it. </think>

The current weather in New York is 65°F with sunny conditions. 🌞 Let me
know if you need additional details!

# User
